Using an iterated block particle filter via \pkg{spatPomp}

### 2024-08-07 ms.Rnw
a few more minor edits

%%%%%% iiiiiiii %%%%
<<bm-model,echo=T,eval=T>>=
library(spatPomp)
i <- 2
b <- bm2(U=4,N=switch(i,10,200),unit_specific_names="rho")
plot(b)
@

@@

Here, \code{i} is a computational intensity switch which adjusts the code for varying run-time.
We set \code{i=1} for testing and debugging, and \code{i=2} for higher quality results.
For simplicity, we consider only one unit-specific parameter, $\rho_{\unit}$, with other parameters being fixed at a value shared between units.
The simulation for \code{b} has $\rho_u=\Sexpr{coef(b)["rho1"]}$ for all $\unit$, but the estimators do not know this.
Before carrying out inference, we check likelihood evaluation.
For this toy model, the \pkg{spatPomp} function \code{bm2\_kalman\_logLik} provides an exact log-likelihood via the Kalman filter.
This study uses a small number of units,
<<define-U,echo=T>>=
U <- 4
@
so that the particle filter is numerically tractable.
We use the particle filter provided by the \pkg{pomp} package \citep{king16}, taking advantage of the class structure where \class{spatPomp} inherits from \class{pomp}.
We can readily validate the agreement between \code{bm2\_kalman\_logLik} and \code{pfilter}, and identify the likelihood cost of the block filter approximation in this situation.

>>>>

%%%%%% iiiiiiii %%%%
<<bm-model,echo=T,eval=T>>=
library(spatPomp)
i <- 2
U <- 4
b <- bm2(U=U,N=switch(i,10,200),unit_specific_names="rho")
plot(b)
@

@@

Here, \code{i} is a computational intensity switch which adjusts the code for varying run-time.
We set \code{i=1} for testing and debugging, and \code{i=2} for higher quality results.
For simplicity, we consider only one unit-specific parameter, $\rho_{\unit}$, with other parameters being fixed at a value shared between units.
The simulation for \code{b} has $\rho_u=\Sexpr{coef(b)["rho1"]}$ for all $\unit$, but the estimators do not know this.
Before carrying out inference, we check likelihood evaluation.
For this toy model, the \pkg{spatPomp} function \code{bm2\_kalman\_logLik} provides an exact log-likelihood via the Kalman filter.
This study uses a small number of units ($U=\Sexpr{U}$) so that the particle filter is numerically tractable.
We use the particle filter provided by the \pkg{pomp} package \citep{king16}, taking advantage of the class structure where \class{spatPomp} inherits from \class{pomp}.
We can readily validate the agreement between \code{bm2\_kalman\_logLik} and \code{pfilter}, and identify the likelihood cost of the block filter approximation in this situation.
